Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems

### 2024-06-14 oup-authoring-template.tex
Add subcaption package

@@

% FIGURE 1
\begin{figure*}[t]

@@

  % \subcaption{\label{fig-first-order}First-order system of an exponential decay. The variable
  % \texttt{x} stores the initial condition for \(x\), and the variable
  % \texttt{eq} stores the rate equation for \(x\).}

@@

  % \subcaption{\label{fig-second-order}Second-order system of an harmonic oscillator, where the
  % variable \texttt{v} stores the derivative \(\frac{dx}{dt}\) and the rate
  % equation is specified for the derivative \texttt{v}.}

@@

  % \subcaption{\label{fig-composition}First-order system of two exponential decays by composition of
  % the \texttt{Decay} system. The subsystem \texttt{linked} has a reference
  % to the outer variable \texttt{x}, while the subsystem
  % \texttt{independent} defines a new variable with initial condition $2$,
  % which on the corresponding mathematical expression was named \(x_{ind}\).}

>>>>

\usepackage{subcaption}

@@

% FIGURE 1
\begin{figure*}[t]
  \begin{minipage}[t]{\linewidth}

@@

  \subcaption{\label{fig-first-order}First-order system of an exponential decay. The variable
  \texttt{x} stores the initial condition for \(x\), and the variable
  \texttt{eq} stores the rate equation for \(x\).}

@@

  \subcaption{\label{fig-second-order}Second-order system of an harmonic oscillator, where the
  variable \texttt{v} stores the derivative \(\frac{dx}{dt}\) and the rate
  equation is specified for the derivative \texttt{v}.}

@@

  \subcaption{\label{fig-composition}First-order system of two exponential decays by composition of
  the \texttt{Decay} system. The subsystem \texttt{linked} has a reference
  to the outer variable \texttt{x}, while the subsystem
  \texttt{independent} defines a new variable with initial condition $2$,
  which on the corresponding mathematical expression was named \(x_{ind}\).}
